Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-01-17 RET_Hosts.tex
Updates from Overleaf

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}

@@

@@

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:sfr_cum}}
\end{figure}

@@

\subsection{Star formation rate \label{subsec:res_sfr}}

@@

>>>>

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}

@@

It is common also to consider metallicity as a factor driving the production of catastrophic stellar explosions. At the extreme end, both GRBs and SLSNe appear to require a low metallicity: for GRBs this threshold has been observed between 0.5 and 1 times the solar value \citep{Perley2016b,Japelj2016,Vergani2017}, while for SLSNe the value is somewhere around half-solar \citep{Lunnan2014,Chen2016a}.

@@

\subsection{Comparison samples \label{subsec:comparison}}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/cum_sSFR_mike.png}
\caption{Cumulative distributions of the sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:ssfr_cum}}
\end{figure}

@@

\subsection{Star formation rate \label{subsec:res_sfr}}
Fig. \ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for CCSNe and for the field galaxies of SDSS. RETs and CCSNe both systematically avoid passive galaxies, suggesting that RETs may require the presence of star-formation and thus be linked to massive stars.

In Fig. \ref{fig:sfr_cum} we show the cumulative distributions of the star-formation rate in RETs, CCSNe, and SDSS galaxies. With the exception of three objects, all RETs occured in galaxies with $\textrm{SFR}>0.1 \msun$yr$^{-1}$, and the curve is shifted towards higher SFRs than that for CCSNe. This would imply that a higher SFR is required for RETs to occur - or can be thought of as a higher SFR threshold for the formation of a RET progenitor.

Fig. \ref{fig:sfms_ssfr} is similar to Fig. \ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming nature of the galaxy itself. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts.

As for SFR, we show the cumulative distribution of sSFR in Fig. \ref{fig:ssfr_cum}. The RET hosts are clearly shifted higher sSFRs than CCSNe. This result is significant as there are no obvious selection effects which could cause the shift.

@@

In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars. A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity. Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we sIn Fig. \ref{fig:mzr}
